### 2016-10-30 IEEEtran/designConcept_GP.tex
added discussion

The cooperatives that are registered for the app are displayed in a map or list view (Figure~\ref{fig:Figure202_Housing_cooperatives_comparison}). Their icons are color coded (from red to green) based on each cooperative's energy performance, i.e. from high to low energy use per heated area, scaled according to the Swedish energy declaration for buildings\footnote{\url{http://www.boverket.se/sv/byggande/energideklaration/energideklarationens-innehall-och-sammanfattning/sammanfattningen-med-energiklasser/energiklasser-fran-ag/}}. 
%  but it is calibrated to only include measured energy use for heating and hot water, which is the greatest part of the energy use. In the Swedish energy declarations, facilities electricity is also added but that often requires estimations of different factors to make the number comparable.
% 
Users can also see the energy performance as a number (in kWh/m$^2$), and the information about energy reduction actions of the cooperatives. %The number of actions is important to display to make energy reduction efforts of housing cooperatives with a high energy performance (e.g. due to poor construction of the building) visible. 
% 
During stakeholder studies, energy managers in cooperative boards stressed the importance of knowing the difference between cooperatives in order to understand the difference in their energy performance. Thus, the design also includes information about cooperatives (Figure~\ref{fig:Figure204_Neighbourhood_average}) such as the number of apartments and heated areas in a cooperative, a building's construction year, and types of ventilations (e.g. with or without heat recovery).
% 
Users can compare a cooperative's energy use per month or per year to another cooperative or to the neighborhood average. The electricity use is also displayed per area (kWh/m$^2$) to make it comparable.
\begin{figure}
\centering
\shadowimage[width=.55\linewidth]{img/brf.pdf}
\caption{Facilities electricity use graph. Information about housing cooperatives and actions is displayed at the top. Green bars show the housing cooperative's current year's use per month; the black line shows the average use of all housing cooperatives}
\label{fig:Figure204_Neighbourhood_average} 
\end{figure}

@@

At the household level, electricity consumption and PV production levels (in W and Wh) are displayed in quasi real-time and updated for the latest six minutes\footnote{For technical reasons such as households' data transfer connections and processing time, there can be up to 2-min delay between the time of actual power measurement and the data displayed.}.
This information can also be displayed as a bar chart for a chosen period (in the past) to provide an aggregated daily overview of consumption vs. production (Figure~\ref{fig:viz_rt}). 
% 
\begin{figure}
      \begin{center}
        \begin{minipage}[htb]{0.4\linewidth}    
        \shadowimage[width=1\linewidth]{img/visual_production.png}
        \end{minipage}
 	\hfill 
         \begin{minipage}[htb]{0.58\linewidth}    
	        \shadowimage[width=1\linewidth]{img/historicalcomparison_prodcons.png} 
                \end{minipage}
      \end{center}
    \caption{(a) Quasi real-time meters for household PV production; (b) Household consumption vs. production for a chosen period
}
\label{fig:viz_rt}
\end{figure}
%
When smart plugs are installed, users can view the daily electricity consumption (in Wh) of the corresponding connected appliances of their own household for a chosen period (Figure~\ref{fig:viz_hist} a). This helps them to gain better insights into the individual appliance's consumption level and its daily or seasonal patterns. 
% Selection of data ranges are mandatory for these visualizations. They must be set by users at two different places: in the ``Energy Data'' main screen for the \textit{Household} category; in the ``light-bulb'' sub-view for the \textit{Appliance} one, which is accessible from the top level bar.
\begin{figure}
      \begin{center}
        \begin{minipage}[htb]{0.48\linewidth}    
        \shadowimage[width=1\linewidth]{img/applianceconsumption.png}
        \end{minipage}
	\hfill 
        \begin{minipage}[htb]{0.49\linewidth}    
         \shadowimage[width=1\linewidth]{img/benchmark.png}
        \end{minipage}
      \end{center}
      \caption{(a) Daily electricity consumption at the appliance level for a chosen period;  (b) 
      A household's hourly consumption profile over a chosen day compared to the averages and totals of the consortia
}
\label{fig:viz_hist}
\end{figure}
 %
With the aggregated energy data provided by the two local electricity consortia, users can also  compare their own households' hourly consumption profiles over a chosen day to the averages and totals of the consortia to gain a sense of their relative performance compared to their peers (Figure~\ref{fig:viz_hist} b).

@@

\subsubsection{Promoting motivation and engagement} 
The design uses a number of elements to promote users' motivation and engagement. 
The suggestions are tailored to the local context by local partners and focus groups. 
Each action is accompanied by a short explanation, the entailed effort and impact (on a five-point scale) and the number of users taking this action. 
The design encourages users to take small steps (and not to have too many actions at a time) and gives positive performance feedback. 
In addition, users can invite household members  (Figure \ref{fig:invite}), view and join the energy conservation actions of the whole household (Figure \ref{fig:form} a).
Users can also login with Facebook, like, comment, share actions (Figure \ref{fig:share}), give feedback (Figure \ref{fig:form} b c) and invite friends. Users are awarded with points  (displayed as Green Leaves) once they complete an action, or provide feedback or comments.

@@

\begin{figure}
      \begin{center}
        \begin{minipage}[t!]{0.33\linewidth}
	       \shadowimage[width=1\linewidth]{img/invite1.jpg}
        \end{minipage}
        %\hfill 
        \begin{minipage}[t!]{0.65\linewidth}    
         \shadowimage[width=1\linewidth]{img/invite2.jpg}
        \end{minipage}
      \end{center}
      \caption{(a) Invite household member; (b) Email invitation}\label{fig:invite}
\end{figure}

@@

\begin{figure}
\centering
\shadowimage[width=0.7\linewidth]{img/share}
\caption{Facebook share of an action}
\label{fig:share}
\end{figure}

@@

>>>>

The cooperatives that are registered for the app are displayed in a map or list view (Figure~\ref{fig:Figure202_Housing_cooperatives_comparison}). Their icons are color coded (from red to green) based on each cooperative's energy performance, i.e. from high to low energy use per heated area, scaled according to the Swedish energy declaration for buildings\footnote{\url{http://www.boverket.se/sv/byggande/energideklaration/energideklarationens-innehall-och-sammanfattning/sammanfattningen-med-energiklasser/energiklasser-fran-ag/}}. 
%  but it is calibrated to only include measured energy use for heating and hot water, which is the greatest part of the energy use. In the Swedish energy declarations, facilities electricity is also added but that often requires estimations of different factors to make the number comparable.
% 
Users can also see the energy performance as a number (in kWh/m$^2$), and the information about energy reduction actions of the cooperatives. %The number of actions is important to display to make energy reduction efforts of housing cooperatives with a high energy performance (e.g. due to poor construction of the building) visible. 
% 
During stakeholder studies, energy managers in cooperative boards stressed the importance of knowing the difference between cooperatives in order to understand the difference in their energy performance. Thus, the design also includes information about cooperatives (Figure~\ref{fig:Figure204_Neighbourhood_average}) such as the number of apartments and heated areas in a cooperative, a building's construction year, and types of ventilations (e.g. with or without heat recovery).
% 
Users can compare a cooperative's energy use per month or per year to another cooperative or to the neighborhood average. The electricity use is also displayed per area (kWh/m$^2$) to make it comparable.
\begin{figure}
\centering
\shadowimage[width=.5\linewidth]{img/brf.pdf}
\caption{Facilities electricity use graph. Information about housing cooperatives and actions is displayed at the top. Green bars show the housing cooperative's current year's use per month; the black line shows the average use of all housing cooperatives}
\label{fig:Figure204_Neighbourhood_average} 
\end{figure}

@@

At the household level, electricity consumption and PV production levels (in W and Wh) are displayed in quasi real-time and updated for the latest six minutes\footnote{For technical reasons such as households' data transfer connections and processing time, there can be up to 2-min delay between the time of actual power measurement and the data displayed.}.
This information can also be displayed as a bar chart for a chosen period (in the past) to provide an aggregated daily overview of consumption vs. production (Figure~\ref{fig:viz_rt}). 
% 
\begin{figure}
      \begin{center}
        \begin{minipage}[htb]{0.4\linewidth}    
        \shadowimage[width=1\linewidth]{img/visual_production.png}
        \end{minipage}
 	\hfill 
         \begin{minipage}[htb]{0.58\linewidth}    
	        \shadowimage[width=1\linewidth]{img/historicalcomparison_prodcons.png} 
                \end{minipage}
      \end{center}
    \caption{(a) Quasi real-time meters for household PV production; (b) Household consumption vs. production for a chosen period
}
\label{fig:viz_rt}
\end{figure}
%
When smart plugs are installed, users can view the daily electricity consumption (in Wh) of the corresponding connected appliances of their own household for a chosen period (Figure~\ref{fig:viz_hist} a). This helps them to gain better insights into the individual appliance's consumption level and its daily or seasonal patterns. 
% Selection of data ranges are mandatory for these visualizations. They must be set by users at two different places: in the ``Energy Data'' main screen for the \textit{Household} category; in the ``light-bulb'' sub-view for the \textit{Appliance} one, which is accessible from the top level bar.
\begin{figure}
      \begin{center}
        \begin{minipage}[htb]{0.48\linewidth}    
        \shadowimage[width=1\linewidth]{img/applianceconsumption.png}
        \end{minipage}
	\hfill 
        \begin{minipage}[htb]{0.45\linewidth}    
         \shadowimage[width=1\linewidth]{img/benchmark.png}
        \end{minipage}
      \end{center}
      \caption{(a) Daily electricity consumption at the appliance level for a chosen period;  (b) 
      A household's hourly consumption profile over a chosen day compared to the averages and totals of the consortia
}
\label{fig:viz_hist}
\end{figure}
 %
With the aggregated energy data provided by the two local electricity consortia, users can also  compare their own households' hourly consumption profiles over a chosen day to the averages and totals of the consortia to gain a sense of their relative performance compared to their peers (Figure~\ref{fig:viz_hist} b).

@@

\subsubsection{Promoting motivation and engagement} 
The design uses a number of elements to promote users' motivation and engagement. 
The suggestions are tailored to the local context by local partners and focus groups. 
Each action is accompanied by a short explanation, the entailed effort and impact (on a five-point scale) and the number of users taking this action. 
The design encourages users to take small steps (and not to have too many actions at a time) and gives positive performance feedback. 
In addition, users can invite household members, %  (Figure \ref{fig:invite}), 
view and join the energy conservation actions of the whole household (Figure \ref{fig:form} a).
Users can also login with Facebook, like, comment, share actions, % (Figure \ref{fig:share}), 
give feedback (Figure \ref{fig:form} b c) and invite friends. Users are awarded with points  (displayed as Green Leaves) once they complete an action, or provide feedback or comments.

@@

%\begin{figure}
%      \begin{center}
%        \begin{minipage}[t!]{0.33\linewidth}
%	       \shadowimage[width=1\linewidth]{img/invite1.jpg}
%        \end{minipage}
%        %\hfill 
%        \begin{minipage}[t!]{0.65\linewidth}    
%         \shadowimage[width=1\linewidth]{img/invite2.jpg}
%        \end{minipage}
%      \end{center}
%      \caption{(a) Invite household member; (b) Email invitation}\label{fig:invite}
%\end{figure}

@@

%\begin{figure}
%\centering
%\shadowimage[width=0.7\linewidth]{img/share}
%\caption{Facebook share of an action}
%\label{fig:share}
%\end{figure}

@@

\section{Discussion}

Co-designed with the stakeholders from the test sites, YouPower provides a set of features that focus on the facilitation of behavior change process towards sustainable energy consumption that is implementable in the context of people's everyday life as a key to address the attitude-behavior gap \cite{Kollmuss2002,Schultz2002,Schultz2014} in people's environmental values (and attitudes) and their actual behavior in energy consumption. From this design experience, a number of design guidelines were derived and are stated in the following, which may be applicable to the development of environmental behavior change interventions beyond the particular case of CIVIS project. First, provide consumers accurate and actionable information about how to achieve the target behavior. At the test sites, people expressed the desire and need to do more for sustainable consumption, and they like the idea of receiving relevant and contextual suggestions and tips for sustainable consumption. 
Second, provide personalized means to motivate consumers to voluntarily practice and repeat the target behavior in the specific context of their everyday life. 
This means that provide personalized target behavior goals and allow users to freely practice and adapt the goals. 
This facilitates the sense of competence and autonomy which promotes and enhances motivation for behavior change. 
Third, foster consumers' intrinsic motivation to engage in the behavior change. 
People are skeptical about how much money they can save by using less energy in households but are driven by intrinsic motives as well as altruistic and environmental values. Social and community-oriented features as those designed in YouPower clearly articulate those values to foster user motivation.

### 2016-10-30 IEEEtran/intro.tex
added discussion

\noindent 
\textit{YouPower} is an open source platform\footnote{\url{http://www.civisproject.eu}, \url{https://app.civisproject.eu}, \url{https://github.com/CIVIS-project}. The packages are available for any
interested party to be reused, modified, and extended under the Apache v.2 License.} designed to explore the potential and challenges of supporting social participation, awareness and engagement of smart gird users for energy conservation and load shifting. Combining smart sensing and web technologies among others,
YouPower features a social smart grid application (developed as a hybrid mobile app) that can connect users to friends, families and local communities to learn and take energy actions that are relevant to them together. The app encourages an energy-friendly lifestyle and can be linked to users' energy consumption and production data for quasi real-time and historical prosumption information. 
% 
The goal of the project is to make energy more visible, to promote environmental and social values, to inform users' know-how about sustainable consumption, and to facilitate users to take energy conservation and load shifting actions in their everyday life together with local communities \cite{Huang2014,Huang2015c,Huang2016}. 
%

>>>>

\noindent 
\textit{YouPower} is an open source platform\footnote{\url{http://www.civisproject.eu}, \url{https://app.civisproject.eu}, \url{https://github.com/CIVIS-project}. The packages are available for any
interested party to be reused, modified, and extended under the Apache v.2 License.} designed to explore the potential and challenges of supporting social participation, awareness and engagement of smart gird users for energy conservation and load shifting. Combining smart sensing and web technologies among others,
YouPower features a social smart grid application (developed as a hybrid mobile app) that can connect users to friends, families and local communities to learn and take energy actions that are relevant to them together. The app encourages an energy-friendly lifestyle and can be linked to users' energy consumption and production data for quasi real-time and historical prosumption information. 
% 
The goal of the project is to make energy more visible, to promote environmental and social values, to inform users' know-how about sustainable consumption, and to facilitate users to take energy conservation and load shifting actions in their everyday life together with local communities \cite{Huang2014,Huang2015a,Huang2016}. 
%

### 2016-10-30 IEEEtran/relatedWork.tex
abstract + conclusion + minor changes
added discussion

The design process of YouPower is theory-driven, user-centered and iterative. We first researched literature on intervention strategies and social smart grid applications directed at promoting environmental behavior change. This provided an initial set of design ideas that had been iteratively refined and improved throughout the design process. 
% 
Applying a user-centered design process can lead to more acceptable, satisfying and effective designs \cite{Brynjarsdottir2012}. This increases the potential of the intervention and may help increase user engagement with respect to the sense of relatedness to the application \cite{dick2012empowering,Pierce2012,schwartz2015people, edward2015review}. 
% 
We organized brainstorming sessions and design workshops with both project partners and users (focus groups) from test sites. A set of features was first prototyped in simple handcrafted mock-ups used as a basis for discussion, and then underwent iterative rapid prototyping which produced wireframes as better visual guides that can be more effectively communicated to users. These wireframe prototypes and later the software prototypes, had been evaluated in iteration by a study with participants during an environmental event in Helsinki \cite{Barssi2015}, by focus groups at test sites, and by groups of students and colleagues. 
% 
Literature research with regard to environmental and social psychology as well as energy intervention had been performed in more depth along with the user studies carried out. Based on those and  the design experiences of the project team, a set of design guidelines had been developed. 
After each study, the design was refined, improved and gradually implemented, resulting in the current version of the application.

>>>>

\noindent The design process of YouPower is theory-driven, user-centered and iterative. We first researched literature on intervention strategies and social smart grid applications directed at promoting environmental behavior change. This provided an initial set of design ideas that had been iteratively refined and improved throughout the design process. 
% 
Applying a user-centered design process can lead to more acceptable, satisfying and effective designs \cite{Brynjarsdottir2012}. This increases the potential of the intervention and may help increase user engagement with respect to the sense of relatedness to the application \cite{dick2012empowering,Pierce2012,schwartz2015people, edward2015review}. 
% 
We organized brainstorming sessions and design workshops with both project partners and stakeholders including users (focus groups) from test sites. A set of features was first prototyped in simple handcrafted mock-ups used as a basis for discussion, and then underwent iterative rapid prototyping which produced wireframes as better visual guides that can be more effectively communicated to users. These wireframe prototypes and later the software prototypes, had been evaluated in iteration by a study with participants during an environmental event in Helsinki \cite{Barssi2015}, by stakeholders at test sites, and by groups of students and colleagues. 
% 
Literature research with regard to environmental and social psychology as well as energy intervention had been performed in more depth along with the user studies carried out. Based on those and  the design experiences of the project team, a set of design guidelines had been developed. 
After each study, the design was refined, improved and gradually implemented, resulting in the current version of the application.
